Evaluating the Decency and Consistency of Data Validation Tests Generated by LLMs

### 2023-10-11 paper/paper.qmd
added my results write up

>>>>

Decency:

Sometimes the LLMs did not generate code, and simply wrote in natural language which expectations to test for. The responses that \"excelled\" in their decency scores tended to bring a new tool beyond what was in the gold standard code suite --  for instance, generating a class with functions, or saving the results as a JSON.

None of the actual tests surpassed the gold standard suite (i.e., testing for something that wasn\'t tested for  in the human written code). Responses that wrote multiple tests for data types or to check that the response is not null were ranked worse than responses with a richer variety of tests. The highest quality tests that the LLMs generated were conditional tests (for instance, checking for a value in a column if the value of another column is X), which are also included in the gold standard suite.

Consistency:

In some cases, one or two results would generate sentences explaining which expectations to test for instead of code, while the other results generated commented code. It was also often the case that results would test for similar things, but one result would write the code slightly different (for instance, using an if statement or a function while testing for the same thing).

The results that scored highest in consistency were exactly identical, or extremely similar with slight variations in comments or tests.

\
